Figures to insert in text

### 2018-03-05 Chapters/Chapter02.tex
sdm + bibtex

$p(H=d)= {2^{-n} \binom{n}{d} } ,$ \\

@@

  INTERPRET PLUS FIG

Another possibility would be to use the sum of all distances closer (and less likely) locations within $w(d)$,

$w(d) = -\log_2 \left( 2^{-n} \displaystyle\sum_{i=0}^{d}{\binom{n}{i}} \right) = n - \log_2 \displaystyle\sum_{i=0}^{d}{\binom{n}{i}}$, \\

@@

@@

Here are some ideas that have been considered during this work, but have had to be left for future research.

@@

@@

\subsection{Symmetrical Hard Locations}

Here is an interesting question that I leave for further research: A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it `belongs to'?  In other words… though this would break Kanerva's assumption of a uniformly distributed set of hard locations for a perfectly symmetrical set of hard locations, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

@@

>>>>

$p(H=d)= {2^{-n} \binom{n}{d} }$ \\

And the probability of it being at most $d$ is \\

@@

Another possibility would be to use the sum of all distances closer (and less likely) locations within the weighting function $w(d)$,

$w(d) = -\log_2 \left( 2^{-n} \displaystyle\sum_{i=0}^{d}{\binom{n}{i}} \right) = n - \log_2 \displaystyle\sum_{i=0}^{d}{\binom{n}{i}}$. \\

@@

Note, finally, that this is not the first time in which a weighted function has been applied to writing in SDM --- \citet{hely1997new} suggest a rather complex spreading model based on floating point signals in the interval [0.05, 1.0] --- they were, however, only able to test their model with 1,000 hard locations.

@@

Here is an interesting questions that have been considered during this work, but have had to be left for future research.

@@

\subsection{i versus l}

\subsection{Magic numbers}

Kanerva suggests, in his book, the use of 1,000 dimensions and 1,000,000 hard locations.  More recently, he suggested the use of 10,000 dimensions.

Each parameter set choice like this will lead to particular numbers --- many of them emergent---, such as the access radius size, critical distance, and so forth.

One intriguing question here is:  is there a `better' number of dimensions and of hard locations?  If so, can such numbers better studied analitically, or numerically?

How should these parameters be compared?  What are the tradeoffs that should be considered?  What are the `best' benchmarks possible?

@@

\subsection{Symmetrical, rapidly accessible, Hard Locations}

A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it `belongs to'?  Though this would break Kanerva's assumption of a randomly yet uniformly distributed set of hard locations --- for a perfectly symmetrical set of hard locations ---, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

$\forall b \in \{ 0,1\} ^n$, we want an algorithm $A$ that yields the particular list of hard locations for $b$ and all hard locations respect the desired properties of the memory.

\subsection{Docker image and jupyter notebooks}

@@

\subsection{From theory to a platform.}

Platforms in the history of computing.

Opens 10 doors.
